Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-23 Papers/ms.tex
Paragraph on computation time etc.

>>>>

We executed the code to generate 3,000 samples from the ``mixture of
constrained priors'' distribution of DNest. Our thinning factor was $10^5$,
so $3 \times 10^8$ MCMC iterations were actually performed, taking approximately
30 hours on a PC purchased new in 2012. After resampling these samples to
reflect the posterior distribution, we were left with 318
(equally weighted) posterior samples.
